Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-23 journal/article.tex
Large scale references

@@

@@

--> [Cockburn 2003] Agile is best suitable for teams around 50 people or fewer.
--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of

--> The company must already be with N teams or N people, not growing up to the
    required numbers. Small companies in growth are therefore excluded.

>>>>

Vlaanderen 2012:
22. Sidky, A.S.: A Structured Approach to Adopting Agile Practices: The Agile Adop-
tion Framework (June 2007)

Cockburn 2003:
R. Crocker, Large-Scale Agile Software Development, Addison-Wesley, 2003.

@@

Elshamy \cite{Elshamy2006}: Roughly speaking, we consider a development project
large if the development team is anywhere between 50 and 100 people (includes
developers, testers, business analysts, and managers).

\cite{Fowler2000}: Cockburn's Crystal methodology has been used by teams of up
to 50 people, but there is little evidence as to how you can use an adaptive
approach, or even if such approaches work at all, beyond that size.

\cite{Williams2003} Agile is best suitable for teams around 50 people or fewer.
A few projects of several hundred people have used the agile framework
succesfully. 9 However, during 2002, agile practitioners and other researchers
concluded that the agile value set and practices best suit colocated teams of
about 50 people or fewer who have easy access to user and business experts and
are developing projects that are not life-critical. Although the agile value set
might be adopted (and may be adapted) under other circumstances, the boundary
conditions for truly agile behavior seem to be fairly set.

@@

--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of

% --> The company must already be with N teams or N people, not growing up to the
%     required numbers. Small companies in growth are therefore excluded.
